### 2015-05-13 whoop.tex
Added a blurn about the soudness of SMACK's emory model.

SMACK then translates the driver from LLVM-IR to Boogie IVL, which is the input language of \whoop. An important feature of SMACK is that it leverages the pointer-alias analyses of LLVM to efficiently model the heap manipulation operations of C programs in Boogie IVL. This means that \whoop does not need to directly deal with pointers and alias analysis, a hard problem on its own, allowing us to re-use robust existing techniques and focus instead on verification efforts.

To achieve scalability, SMACK uses a \emph{split} memory model that exploits the case where
alias analysis asserts that a given memory location cannot be aliased by multiple types.
This has been shown to lead to more tractable verification compared with a \emph{monolithic} model where the heap is considered to be an array of bytes~\cite{rakamaric2009scalable}. This split memory model is based on \emph{memory regions}, which are maps of integers that model the heap. A benefit of using this model is that distinct memory regions denote disjoint sections of the heap. We leverage this knowledge inside \whoop to guide and optimize our lockset instrumentation and analysis, and to create a fine-grained context-switch instrumentation as discussed in \S\ref{corral}.

>>>>

SMACK then translates the driver from LLVM-IR to Boogie IVL, which is the input language of \whoop. An important feature of SMACK is that it leverages the pointer-alias analyses of LLVM to efficiently model the heap manipulation operations of C programs in Boogie IVL. This means that \whoop does not need to directly deal with pointers and alias analysis, a hard problem on its own, allowing us to reuse robust existing techniques and focus instead on verification efforts.

To achieve scalability, SMACK uses a \emph{split} memory model that exploits an alias analysis to soundly partition memory locations into non-overlapping equivalence classes that do not alias. This has been shown to lead to more tractable verification compared with a \emph{monolithic} model where the heap is considered to be an array of bytes~\cite{rakamaric2009scalable}. The split memory model is based on \emph{memory regions}, which are maps of integers that model the heap. A benefit of using this model is that distinct memory regions denote disjoint sections of the heap. We leverage this knowledge inside \whoop to guide and optimize our lockset instrumentation and analysis, and to create a fine-grained context-switch instrumentation as discussed in \S\ref{corral}. Note that the SMACK's memory model can potentially be unsound in (typically rare) situations where programs use unaligned byte-level memory accesses. The latest release of SMACK addresses this issue, and as future work we plan to integrate the latest SMACK with \whoop to further improve soundness.
